\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-02-13 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Problem set-up}\label{problem_set_up}      
Multiphase flow in porous media is described by mass conversation (or transport) equation and Darcy velovities for each of the phase $\alpha$ ($\alpha$ = g, o, w, for gas, oil, and water phases).
Fingering behaviour is expected to be different from single-phase (piston shape front) due to the effect of different peremeabilities. This will change the mobility contrast between two phases for a given \textit{viscosity} ratio. Because of the  different saturation levels among different layers, eventually this will enhance the flow instabilities. In this paper, the test-cases are also based on the discontinuous Galerkin (DG) method to simulate viscous fingering. Roughly speaking, DG-method combines advantages of classical finite volume and finite element methods.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Governing equations and numerical scheme}\label{equations_scheme}      
Multiphase flow in porous media is described by mass conversation (or transport) equation and Darcy velovities for each of the phase $\alpha$ ($\alpha$ = g, o, w, for gas, oil, and water phases).
Fingering behaviour is expected to be different from single-phase (piston shape front) due to the effect of different peremeabilities. This will change the mobility contrast between two phases for a given \textit{viscosity} ratio. Because of the  different saturation levels among different layers, eventually this will enhance the flow instabilities. In this paper, the test-cases are also based on the discontinuous Galerkin (DG) method to simulate viscous fingering. Roughly speaking, DG-method combines advantages of classical finite volume and finite element methods.
